Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex
paper: minor modifications

Preferences \cite{Peintner2008} play an important role in artificial intelligence,
including fields spanning from recommender systems to automatic planning, 
from non monotonic reasoning to computational social choice and algorithmic decision theory.
The task of eliciting or learning preferences is therefore a crucial; typically only limited information about the user's preferences will be available and the cost of obtaining additional preference information will be high (from a cognitive and/or computational point of view).
The goal in preference elicitation is that of gaining enough information about the user's preferences %(typically represented by an utility function $u$, unknown to the system) 
in order to recommend a decision or a course of action.

The assessment of preferences have received considerable attention in the literature, with early works confined to the operation research and management literature mostly \cite{White1984,JacquetLagreze95}.
%In the past decade a number of researchers have considered elicitation of preferences from an artificial intelligence perspective%; within the machine learning field the term preference learning has been catching up.
%While preferences are often assessed using some ad-hoc rules \cite{},
Recently, in the last decade or so, a number of artificial intelligence researchers have proposed principled methods that elicit utility in an adaptive way \cite{chajewska2000,boutilier2002,Wang2003,boutilier2006,braziunas2007,guo2010real,viappiani2010optimal}; the aims is that of focusing on learning the ``important'' part of the utility, allowing to recommend good (or even optimal) decision with only a partial information about the utility function.

@@

Preference elicitation in configuration problems has been previously tackled with regret-based elicitation \cite{boutilier2006,braziunas2007}, where minimax regret is used both
as a robust recommendation criterion and as a technique to drive elicitation in configuration problems.
The main limitation of the minimax regret approach is the lack of tolerance with respect to user inconsistency (the user might state that an item is preferred to another one, even though the latter has higher utility).

% setwise max-margin formulation to deal with uncertainty in user utility
Indeed, learning a user utility function requires setting a preference
elicitation strategy and dealing with uncertain and possibly
inconsistent user feedback. 
Bayesian preference elicitation approaches
deal with both problems by building a probability distribution on
candidate functions (endowed with a response or error model to be used for inference) and asking queries maximizing informativeness
measures such as expected value of information (EVOI)~\cite{chajewska2000,guo2010real,viappiani2010optimal}.

These
approaches are however computationally expensive and can not scale to
fully constructive scenarios, as shown in our experimental results.
We take a space decomposition perspective and jointly learn a set of
weight vectors, each representing a candidate utility function,
maximizing diversity between the vectors and consistency with the
available feedback. These two conflicting objectives tend to generate
equally plausible alternative hypotheses for the unknown
utility. 
Our approach to preference elicitation works by combining weight vector
learning with instance generation, so that each iteration of the
algorithm produces two outcomes: a set of weight vectors and a set of
instances, each maximizing its score according to one of the weight
vectors.

We evaluate the effectiveness of our approach by testing our elicitation method
in both synthetic and configuration problems, and comparing it to state-of-the-art
methods.

The paper is structured as follows: after discussing related works in next Section,
we present some background material in Section \ref{sec:background} 
and then proceed to our setwise maxmargin method in Section \ref{sec:formulation}; 
we discuss experimental results in Section \ref{sec:experiments}
and conclude with final remarks (Section \ref{sec:conclusions}).

@@

Consistently with previous work~\cite{guo2010real,viappiani2010optimal}, 
we model users by means of utility functions of a given structure; the user's preferences are represented by a latent weight
vector $\vw\in\bbR^m$.
We assume linear utility functions; the utility of a configuration $\vx$ is given by
$\langle \vw, \vx \rangle = \sum_{z=1}^m w_z x_z$
(see \cite{keeney1976} for theoretical conditions justifying additive utility functions). 
In the remainder of the paper we
require all weights to be {\em non-negative} and {\em bounded}: the per-attribute
weights $w_z$ must lie in a (constant but otherwise arbitrary) interval
$[w^\bot_z, w^\top_z]$, with $w^\bot_z \ge 0$. 
Both requirements are quite natural\footnote{Utility values are defined on an
interval scale, therefore the assumption of non negativity is not restrictive as it is always possible to scale the values appropriately (see for instance \cite{Torra2007} and \cite{keeney1976}).}, and enable the translation of our core optimization problem into a
mixed-integer linear problem (as done in Section~\ref{sec:formulation}).

During learning, the actual weight vector $\vw$ is {\em unknown} to the
learning system, and must be estimated from pairwise choices elicited from the
user.
%\andrea{@PAOLO: qualche parola e reference per giustificare la scelta di pairwise queries?}  
Comparison queries are especially natural, asking a user if she prefers one option x to another y;
these comparisons can be extended to choice sets of more than two options \cite{viappiani2009,viappiani2010optimal}.
Comparison and choice queries are common in conjoint analysis \cite{louviere2000,toubia2004}.

We consider three possible outcomes for a pairwise comparison between
two configurations $\vx$ and $\vx'$: either $\vx$ is preferred to $\vx'$ (written
$\vx \succ \vx'$), $\vx'$ is preferred to $\vx$ ($\vx \prec \vx'$), or there is
no clear preference between the two items ($\vx \approx \vx'$). We write
$\calD$ to denote the set of preferences (answers to comparison queries) 
elicited from the user. Queries are typically selected so as to maximize 
some measure of informativeness of the
resulting responses.  Details on our actual query selection strategy will be
provided in Section~\ref{sec:formulation}.

@@

The goal of our setwise max-margin approach is twofold. First, for any
given set size $k\geq 1$, we want to find a {\em set} of $k$ weight
vectors $\vw^{1}, \ldots, \vw^{k}$, chosen so that all user-provided
preferences are satisfied by the largest possible margin (i.e. all
weight vectors are consistent with respect to the user responses
$\calD$, modulo inconsistencies) and so that they are maximally
diverse.  Second, we want to construct a {\em set} of $k$
configurations $\vx^{1}, \ldots, \vx^{k}$, so that each configuration
$\vx^{i}$ is the ``best'' possible option when evaluated according to
the corresponding $\vw^{i}$ and configurations are maximally diverse
among each other. These options will be later employed to formulate
the user queries.

The first goal is achieved by translating all pairwise preferences
$\calD$ into ranking constraints: preferences of the form
$\vy^h_+ \succ \vy^h_-$ become linear inequalities of the form
$\langle \vw^i, \vy^h_+ - \vy^h_- \rangle \geq \mu$, where $\mu$ is the
{\em margin} variable (which we aim at maximizing) and $h$ ranges over
the responses.  Non-separable datasets, which occur in practice due to
occasional inconsistencies in user feedback, are handled by
introducing slack variables (whose sum we aim at minimizing). When
augmented with the slacks, the above inequalities take the form:
\begin{align*}
\langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h 
\end{align*}
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector $\vw^{i}$
for violating the margin separation of pair $h$. Indifference preferences, i.e.
$\vy^h_1 \approx \vy^h_2$, are translated as $|\langle \vw^i, \vy^h_1 - \vy^h_2 \rangle| < \varepsilon^i_h$;
the slack increases with the difference between the estimated utility of the
two options.

@@

A straightforward encoding of the above desiderata leads to the
following mixed integer {\em non-linear} optimization problem over the
variables $\mu \in \bbR$, $\{ \vw^i \in \bbR^m \}$, $\{ \vx^i \in \{0,1\}^m \}$:
%
{\footnotesize
\begin{align}
    \max
        & \;\; \mu - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \quad \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge \mu \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \quad \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \veps^{i} \ge 0 \nonumber
    \\
        & \;\; \mu \ge 0 \nonumber
\end{align}
}
%
Let us illustrate the above piece by piece. The objective is composed of four
parts: we maximize the shared margin $\mu$ (first part) and minimize the total
sum of the ranking errors $\veps^i$ incurred by each weight vector $\vw^{i}$
(second part), while at the same time regularizing the magnitude of the
weights (third part) and the quality of the configurations $\{ \vx^{i} \}$ (last
part). The non-negative hyperparameters $\alpha,\beta,\gamma$ control the
influence of the various components.

The third part of the objective does require a more in depth explanation. In
many scenarios the user will have strong preferences about some attributes, but
will be indifferent to most of them. %~\cite{} \stefano{@Paolo: add refs}. 
The $\ell_1$ penalty is frequently
used to improve the sparsity of learned models~\cite{lasso,zhang2008,Hensinger2010}, with consequent gains
in generalization ability and efficiency, as confirmed by our empirical
findings (see Section~\ref{sec:experiments}).

@@

Note that we are choosing the configurations $\{ \vx^i \}$ and the weight vectors $\{
\vw^i \}$ {\em simultaneously}.
Look at Figure~\ref{fig:setmargin}, where, for simplicity, we need to choose a pair ($k=2$). 
The constraint \ref{eq:wxconstr} is represented by a red line, that partitions the space of
feasible utility weights in two parts (in general, there will be $k$ subregions).
Since we maximize the margin $\mu$, the optimizer
will prefer a set of configurations $\{ \vx^{1}, \vx^{2} \}$ that partitions the weight space
in an even way.
In each subregion, we have corresponding utility weight vector $\vw^{i}$
lying ``close'' to the centre of each subregion. 
Note that if we present $\vx^{1}$ and $\vx^{2}$ to the user, and the user states that he prefers
the former to the latter, the feasible region for the weights will then become the part of the polytope to the left of the red line; moreover $\vw^{1}$ will be vector maximizing the margin in the classic sense.
Therefore, setwise maxmargin can be thought as a ``look-ahead'' model with respect to a standard ($k=1$) max margin learner a posteriori.
%Therefore, setwise maxmargin can be thought as the set that, given any possible preference about the items, ensure that the reduction of utility uncertainty is the greatest
\paolo{ho fatto un tentativo di migliorare l'intuizione, ma e' ancora possibile migliorare...}

@@

\paolo{Se bisogno di spazio, posso accorciare la descrizione.}
\begin{itemize}
\item The best Bayesian approach from \cite{guo2010real}, selecting
  queries according to {\em restricted informed VOI} ({\sc riVOI}), a
  heuristic approximation of value-of-information, and performing
  inference using TrueSkill$^{TM}$ \cite{HerbrichMG06} (an inference
  scheme based on expectation propagation \cite{Minka01}).

 \item The Bayesian framework of \cite{viappiani2010optimal} using Monte Carlo methods for Bayesian inference and asking choice queries (asking the user to select its preferred item among a set of diplayed ones); the next query is computed by performing a greedy optimization of {\em Expected Utility of a Selection} (hereafter just called {\sc EUS}), a submodular quantity that can be used as a proxy for value of information (giving strong approximate guarantees).

 \item {\em Query Iteration} (referred as {\sc QI} below), also from \cite{viappiani2010optimal}, an even faster query selection method based on sampling a set of utility vectors, selecting the items that maximize utility for each of the vector, forming a first proposal for a query set. Then, a new set is computed by considering the optimal items in the associated  beliefs, and the process is repeated until convergence.
\end{itemize}

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. According to the classical
(without indifference) Bradley-Terry model~\cite{BraTer52}, when queried about a pair
of configurations, the probability that a user will prefer
configuration $\vx^i$ over the alternative $\vx^j$ amounts to:
%
$$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
where $\vw$ is the weight vector of the true underlying user utility.
In other words, the probability grows with the difference between the
utilities of the two items. Support for indifference has been
introduced in~\cite{guo2010real} by postulating that the probability
of the user being indifferent about the two configurations depends on
how close their utilities are, as in the exponential distribution:
%
$$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|). $$
%
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations\footnote{When experiment with EUS and QI, the user is forced to select
its preffered item, so indifference is not possible. While support for indifference
could be added, we chose to .}, as in~\cite{guo2010real}.

@@

\paragraph{Synthetic Dataset.} Following the experimental protocol
in~\cite{guo2010real} and \cite{viappiani2010optimal}, in the first
experiment we evaluate the behavior of the proposed method in an
artificial setting with increasingly complex problems. We developed
synthetic datasets with $r$ attributes, for increasing values of $r$.
Each attribute takes one of $r$ possible values, so that the one-hot
encoding of attributes results in $m=r^2$ features. In terms of space
of configurations, for $r=3$ the synthetic dataset corresponds to 
$\calX_\text{feasible} = [3] \times [3] \times [3]$, for $r=4$ to
$\calX_\text{feasible} = [4] \times [4] \times [4] \times [4]$, and so on. The
cardinality of $\calX_\text{feasible}$ is $r^r$, and grows (super)
exponentially with $r$.
% We developed
% seven synthetic datasets: each dataset involves $m=2,\ldots,7$
% attributes, where each attribute takes one of $m$ possible
% values. More explicitly, for $m=2$ the synthetic dataset is
% $\calX_\text{feasible} = [2] \times [2]$, for $m=3$ to
% $\calX_\text{feasible} = [3] \times [3] \times [3]$, and so on. The
% cardinality of $\calX_\text{feasible}$ is $m^m$, and grows (super)
% exponentially with $m$. 
For $r=3$, the dataset is comparable to the synthetic one used
in~\cite{guo2010real} and~\cite{viappiani2010optimal}, which have
three attributes with 2, 2 and 5 values respectively, for a total of
20 feasible configurations.  For larger $r$ the size of the space
grows much larger than the one typically used in the Bayesian
preference elicitation literature, and as such represents a good testbed
for comparing the scalability of the various methods. The feasible
configuration space was encoded in {\sc SetMargin} through appropriate
MILP constraints, while the other methods require all datasets to be
explicitly grounded.

Users were simulated by drawing $20$ random utility vectors from each of four
different distributions. The first two mimic those used
in~\cite{guo2010real}\footnote{The normal distribution reported
in~\cite{guo2010real} differs slightly from the one implemented in the code of
their experimental setting. 
In our experiments we use the latter.}:
(1) a uniform distribution over $[1, 100]$ for each individual weight, and (2)
a normal distribution with mean $25$ and %covariance
standard deviation $\frac{25}{3}$ (each attribute is sample i.i.d).  
We further produced two novel
{\em sparse} sets of weight vectors by setting to zero $80\%$ of the entries of the
vectors sampled in the uniform and normal settings uniformly at random. 
All methods were evaluated on the very same weight vectors. All users had
a budget of 100 iterations; for {\sc SetMargin} we used a $0.01$
threshold on the utility loss for early stopping (that does not affect the
cross-validation procedure).
The Bayesian methods can use the estimated loss to decide when to stop (the expectation
of the utility loss with respect to the current probabilistic belief)
\footnote{In our experiments, we left the Bayesian methods to run the full amount of iterations,
even when the estimated loss was very low.}.

>>>>

Preferences \cite{Peintner2008} play an important role in artificial
intelligence, including fields spanning from recommender systems to
automatic planning, from non monotonic reasoning to computational
social choice and algorithmic decision theory.  The task of eliciting
or learning preferences is therefore a crucial one; typically only limited
information about the user's preferences will be available and the
cost of obtaining additional preference information will be high (from
a cognitive and/or computational point of view).  The goal in
preference elicitation is that of gaining enough information about the
user's
preferences %(typically represented by an utility function $u$, unknown to the system)
in order to recommend a decision or a course of action.

The assessment of preferences have received considerable attention in the literature, with early works confined to the operation research and management literature mostly \cite{White1984,JacquetLagreze95}.
%In the past decade a number of researchers have considered elicitation of preferences from an artificial intelligence perspective%; within the machine learning field the term preference learning has been catching up.
%While preferences are often assessed using some ad-hoc rules \cite{},
Recently, in the last decade or so, a number of artificial
intelligence researchers have proposed principled methods that elicit
utility in an adaptive way
\cite{chajewska2000,boutilier2002,Wang2003,boutilier2006,braziunas2007,guo2010real,viappiani2010optimal}. The
aim is that of focusing on learning the ``important'' part of the
utility, allowing to recommend good (or even optimal) decisions with
only partial knowledge of the utility function.

@@

Preference elicitation in configuration problems has been previously
tackled with regret-based elicitation
\cite{boutilier2006,braziunas2007}, where minimax regret is used both
as a robust recommendation criterion and as a technique to drive
elicitation in configuration problems.  The main limitation of the
minimax regret approach is the lack of tolerance with respect to user
inconsistency (the user might state that an item is preferred to
another one, even though the latter has higher utility).
% setwise max-margin formulation to deal with uncertainty in user utility

Indeed, learning a user utility function requires setting a preference
elicitation strategy and dealing with uncertain and possibly
inconsistent user feedback.  Bayesian preference elicitation
approaches deal with both problems by building a probability
distribution on candidate functions (endowed with a response or error
model to be used for inference) and asking queries maximizing
informativeness measures such as expected value of information
(EVOI)~\cite{chajewska2000,guo2010real,viappiani2010optimal}.  These
approaches are however computationally expensive and can not scale to
fully constructive scenarios, as shown in our experimental results.

We take a space decomposition perspective and jointly learn a set of
weight vectors, each representing a candidate utility function,
maximizing diversity between the vectors and consistency with the
available feedback. These two conflicting objectives tend to generate
equally plausible alternative hypotheses for the unknown
utility. 
Our approach to preference elicitation works by combining weight vector
learning with instance generation, so that each iteration of the
algorithm produces two outcomes: a set of weight vectors and a set of
instances, each maximizing its score according to one of the weight
vectors.

We evaluate the effectiveness of our approach by testing our
elicitation method in both synthetic and real-world problems, and
comparing it to state-of-the-art methods.

The paper is structured as follows: we present some background
material in Section \ref{sec:background} and then proceed to our
setwise max-margin method in Section \ref{sec:formulation}; we discuss
experimental results in Section \ref{sec:experiments} and conclude
with final remarks (Sec.~\ref{sec:conclusions}).

@@

Consistently with previous work~\cite{guo2010real,viappiani2010optimal}, 
we model users by means of utility functions of a given structure; the user's preferences are represented by a latent weight
vector $\vw\in\bbR^m$.
We assume linear utility functions; the utility of a configuration $\vx$ is given by
$\langle \vw, \vx \rangle = \sum_{z=1}^m w_z x_z$
(see \cite{keeney1976} for theoretical conditions justifying additive utility functions). 
In the remainder of the paper we
require all weights to be {\em non-negative} and {\em bounded}: the per-attribute
weights $w_z$ must lie in a (constant but otherwise arbitrary) interval
$[w^\bot_z, w^\top_z]$, with $w^\bot_z \ge 0$. 
Both requirements are quite natural\footnote{Utility values are defined on an
interval scale, therefore the assumption of non negativity is not restrictive as it is always possible to scale the values appropriately (see for instance \cite{Torra2007} and \cite{keeney1976}).}, and enable the translation of our core optimization problem into a
mixed-integer linear problem (as done in Section~\ref{sec:formulation}). 
%\andrea{@paolo: sulla giustificazione delle utilita' additive, vogliamo metterla? c'e' anche molto lavoro che contesta il fatto che basti no?}

During learning, the actual weight vector $\vw$ is {\em unknown} to
the learning system, and must be estimated by interacting with the
user. We mostly focus on pairwise comparison queries, which are the
simplest of the comparative queries. These can be extended to choice
sets of more than two options
\cite{viappiani2009,viappiani2010optimal}.  Comparison and choice
queries are common in conjoint analysis
\cite{louviere2000,toubia2004}. We consider three possible outcomes
for a pairwise comparison between two configurations $\vx$ and $\vx'$:
either $\vx$ is preferred to $\vx'$ (written $\vx \succ \vx'$), $\vx'$
is preferred to $\vx$ ($\vx \prec \vx'$), or there is no clear
preference between the two items ($\vx \approx \vx'$). We write
$\calD$ to denote the set of preferences (answers to comparison
queries) elicited from the user. Queries are typically selected so as
to maximize some measure of informativeness of the resulting
responses.  Details on our actual query selection strategy will be
provided in Section~\ref{sec:formulation}.

@@

The goal of our setwise max-margin approach is twofold. First, for any
given set size $k\geq 1$, we want to find a {\em set} of $k$ weight
vectors $\vw^{1}, \ldots, \vw^{k}$, chosen so that all user-provided
preferences are satisfied by the largest possible margin (%
%i.e. all
%weight vectors are consistent with respect to the user responses
%$\calD$, 
modulo inconsistencies) and so that they are maximally
diverse.  Second, we want to construct a {\em set} of $k$
configurations $\vx^{1}, \ldots, \vx^{k}$, so that each configuration
$\vx^{i}$ is the ``best'' possible option when evaluated according to
the corresponding $\vw^{i}$ and configurations are maximally diverse
among each other. These options will be later employed to formulate
the user queries.

The first goal is achieved by translating all pairwise preferences
$\calD$ into ranking constraints: preferences of the form
$\vy^h_+ \succ \vy^h_-$ become linear inequalities of the form
$\langle \vw^i, \vy^h_+ - \vy^h_- \rangle \geq \mu$, where $\mu$ is the
{\em margin} variable (which we aim at maximizing) and $h$ ranges over
the responses.  Non-separable datasets, which occur in practice due to
occasional inconsistencies in user feedback, are handled by
introducing slack variables (whose sum we aim at minimizing). When
augmented with the slacks, the above inequalities take the form
$\langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h$
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector $\vw^{i}$
for violating the margin separation of pair $h$. Indifference preferences, i.e.
$\vy^h_1 \approx \vy^h_2$, are translated as $|\langle \vw^i, \vy^h_1 - \vy^h_2 \rangle| < \varepsilon^i_h$;
the slack increases with the difference between the estimated utility of the
two options.

@@

A straightforward encoding of the above desiderata leads to the
following mixed integer {\em non-linear} optimization problem over the
variables $\mu \in \bbR$, $\{ \vw^i \in \bbR^m \}$, $\{ \vx^i \in \{0,1\}^m \}$:
%
{\footnotesize
\begin{align}
    \max
        & \;\; \mu - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \quad \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge \mu \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \quad \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \veps^{i} \ge 0 \nonumber
    \\
        & \;\; \mu \ge 0 \nonumber
\end{align}
}
%
Let us illustrate the above piece by piece. The objective is composed
of four parts: we maximize the shared margin $\mu$ (first part) and
minimize the total sum of the ranking errors $\veps^i$ incurred by
each weight vector $\vw^{i}$ (second part), while at the same time
regularizing the magnitude of the weights (third part) and the quality
of the configurations $\{ \vx^{i} \}$ (last part). The non-negative
hyperparameters $\alpha,\beta,\gamma$ control the influence of the
various components. The weight regularization term copes with the
common scenario in which the user has strong preferences about
some attributes, but is indifferent to most of
them. %~\cite{} \stefano{@Paolo: add refs}.
The $\ell_1$ penalty is frequently used to improve the sparsity of
learned models~\cite{lasso,zhang2008,Hensinger2010}, with consequent
gains in generalization ability and efficiency, as confirmed by our
empirical findings (see Section~\ref{sec:experiments}).

@@

Note that we are choosing the configurations $\{ \vx^i \}$ and the weight vectors $\{
\vw^i \}$ {\em simultaneously}.
Look at Figure~\ref{fig:setmargin}, where, for simplicity, we need to choose a pair ($k=2$). 
The constraint \ref{eq:wxconstr} is represented by a red line, that partitions the space of
feasible utility weights in two parts (in general, there will be $k$ subregions).
Since we maximize the margin $\mu$, the optimizer
will prefer a set of configurations $\{ \vx^{1}, \vx^{2} \}$ that partitions the weight space
in an even way.
In each subregion, we have corresponding utility weight vector $\vw^{i}$
lying ``close'' to the centre of each subregion. 
Note that if we present $\vx^{1}$ and $\vx^{2}$ to the user, and the user states that he prefers
the former to the latter, the feasible region for the weights will then become the part of the polytope to the left of the red line; moreover $\vw^{1}$ will be vector maximizing the margin in the classic sense.
Therefore, setwise maxmargin can be thought as a ``look-ahead'' model with respect to a standard ($k=1$) max-margin learner a posteriori.
%Therefore, setwise maxmargin can be thought as the set that, given any possible preference about the items, ensure that the reduction of utility uncertainty is the greatest
%\paolo{ho fatto un tentativo di migliorare l'intuizione, ma e' ancora possibile migliorare...}
%\andrea{cosa intendi per a posteriori?}

@@

\begin{itemize}
\item The best Bayesian approach from \cite{guo2010real}, selecting
  queries according to {\em restricted informed VOI} ({\sc riVOI}), a
  heuristic approximation (equally effective but more efficient) of
  value-of-information, and inference using TrueSkill$^{TM}$
  \cite{HerbrichMG06} (an inference scheme based on expectation
  propagation \cite{Minka01}).

 \item The Bayesian framework of \cite{viappiani2010optimal} using Monte Carlo methods for Bayesian inference and asking choice queries (asking the user to select its preferred item among a set of displayed ones); the next query is computed by performing a greedy optimization of {\em Expected Utility of a Selection} (hereafter just called {\sc EUS}), a submodular quantity that can be used as a proxy for value of information (giving strong approximate guarantees).

 \item {\em Query Iteration} (referred as {\sc QI} below), also from \cite{viappiani2010optimal}, an even faster query selection method based on sampling a set of utility vectors, selecting the items that maximize utility for each of the vector and forming a first proposal for a query set. Then, a new set is computed by considering the optimal items in the associated  beliefs, and the process is repeated until convergence.
\end{itemize}

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. According to the classical
(without indifference) Bradley-Terry model~\cite{BraTer52}, when queried about a pair
of configurations, the probability that a user will prefer
configuration $\vx^i$ over the alternative $\vx^j$ amounts to:
%
$$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
where $\vw$ is the weight vector of the true underlying user utility.
In other words, the probability grows with the difference between the
utilities of the two items. Support for indifference has been
introduced in~\cite{guo2010real} by postulating that the probability
of the user being indifferent about the two configurations depends on
how close their utilities are, as in the exponential distribution:
%
$$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|). $$
%
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations, as in~\cite{guo2010real}.

% \footnote{When experiment with EUS and QI, the user is forced to select
% its preffered item, so indifference is not possible. While support for indifference
% could be added, we chose to .}
%\andrea{@paolo: e' necessaria la footnote? dobbiamo tagliare..}

@@

\paragraph{Synthetic Dataset.} Following the experimental protocol
in~\cite{guo2010real} and \cite{viappiani2010optimal}, in the first
experiment we evaluate the behavior of the proposed method in an
artificial setting with increasingly complex problems. We developed
synthetic datasets with $r$ attributes, for increasing values of $r$.
Each attribute takes one of $r$ possible values, so that the one-hot
encoding of attributes results in $m=r^2$ features. In terms of space
of configurations, for $r=3$ the synthetic dataset corresponds to 
$\calX_\text{feasible} = [3] \times [3] \times [3]$, for $r=4$ to
$\calX_\text{feasible} = [4] \times [4] \times [4] \times [4]$, and so on. The
cardinality of $\calX_\text{feasible}$ is $r^r$, and grows (super)
exponentially with $r$.
% We developed
% seven synthetic datasets: each dataset involves $m=2,\ldots,7$
% attributes, where each attribute takes one of $m$ possible
% values. More explicitly, for $m=2$ the synthetic dataset is
% $\calX_\text{feasible} = [2] \times [2]$, for $m=3$ to
% $\calX_\text{feasible} = [3] \times [3] \times [3]$, and so on. The
% cardinality of $\calX_\text{feasible}$ is $m^m$, and grows (super)
% exponentially with $m$. 
For $r=3$, the dataset is comparable in size to the synthetic one used
in~\cite{guo2010real} and~\cite{viappiani2010optimal}.
%, which have
%three attributes with 2, 2 and 5 values respectively, for a total of
%20 feasible configurations.  
For larger $r$ the size of the space grows much larger than the one
typically used in the Bayesian preference elicitation literature, and
as such represents a good testbed for comparing the scalability of the
various methods. The feasible configuration space was encoded in {\sc
  SetMargin} through appropriate MILP constraints, while the other
methods require all datasets to be explicitly grounded.

Users were simulated by drawing $20$ random utility vectors from each
of four different distributions. The first two mimic those used
in~\cite{guo2010real}\footnote{The normal distribution reported
  in~\cite{guo2010real} differs slightly from the one implemented in
  the code of their experimental setting.  In our experiments we use
  the latter.}: (1) a uniform distribution over $[1, 100]$ for each
individual weight, and (2) a normal distribution with mean $25$
and %covariance
standard deviation $\frac{25}{3}$ (each attribute is sample i.i.d).
We further produced two novel {\em sparse} versions of the uniform and
normal distributions setting to zero $80\%$ of the entries (sampled
uniformly at random). All methods were evaluated on the same weight
vectors. All users had a budget of 100 iterations; for {\sc SetMargin}
we used a $0.01$ threshold on the utility loss for early stopping
(that does not affect the cross-validation procedure).  The Bayesian
methods can use the estimated loss to decide when to stop (the
expectation of the utility loss with respect to the current
probabilistic belief) \footnote{In our experiments, we left the
  Bayesian methods to run the full amount of iterations, even when the
  estimated loss was very low.}. \andrea{@stefano: cosi' non va. O tutti early stopping o nessuno..}
